Lab journal

### 2024-11-25 finaldata.Rmd
finalpushh

---
title: "Data & Analysis"
author: "Verooo"
date: "2024-11-23"
output: html_document
bibliography: references.bib
csl: apa.csl
editor_options: 
  markdown: 
    wrap: 72
---

>>>>

---
title: "Data & Analysis"
author: "Vero Palm"
date: "2024-11-23"
output: html_document
bibliography: references.bib
csl: apa.csl
editor_options: 
  markdown: 
    wrap: 72
---

### 2024-11-25 finalestimate.Rmd
finalpushh

---
title: "Model Estimation"
author: "Verooo"
date: "2024-11-23"
output: html_document
bibliography: references.bib
csl: apa.csl
editor_options: 
  markdown: 
    wrap: 72
---

>>>>

---
title: "Model Estimation"
author: "Vero Palm"
date: "2024-11-23"
output: html_document
bibliography: references.bib
csl: apa.csl
editor_options: 
  markdown: 
    wrap: 72
---

### 2024-11-25 index.Rmd
finalpushh

---
title: "Lab journal"
author: "by: Verooo"
bibliography: references.bib
---

@@

::: columns
::: {.column width="50%"}
# First page of something totally awesome yes.

@@

Last compiled on `r format(Sys.time(), '%B, %Y')`

*Description: Very cool lab journal. Yes, yes.*

```{=html}
<!--- The ---- is a visual line (page break looking mf) on the 
website 
Always ADD A SPACE BETWEEN A PAGE BREAK AND the next comment, otherwise it will appear on page --->
```
```{=html}
<!--- This is the best way to write a comment. 
It also demonstrates, you can add html directly in your rmarkdown file. See: https://www.w3schools.com/html/html_comments.asp --->
```
```{=html}
<!--- to use a multi column page we use Pandoc's fenced Div. 
see here: https://bookdown.org/yihui/rmarkdown-cookbook/multi-column.html 
But please note, we are not here to make a beautiful website, our intention is just to have a quick lab journal up and running --->
```
## Open Science

Everyone can fork this repository. Use this example to journal your lab work and assignments.

We, Jochem Tolsma and Bas Hofstra, use this repository for our Social Network Analysis For Social Scientists course [@SNASS]. <!--- this is a reference, stored in references.bib. It will be automatically added at the bottom of the page --->

treeeeees
:::

::: {.column width="50%"}
![](images/krill-issue.jpg)
:::
:::

>>>>

---
title: "Lab journal"
author: "by: Vero Palm"
bibliography: references.bib
---

@@

::: columns
::: {.column width="50%"}
# First page of something totally awesome yes.
Last compiled on `r format(Sys.time(), '%B, %Y')`
*Description: Very cool lab journal. Yes, yes.*

## Cool keybinds

@@

```{=html}
<!--- The ---- is a visual line (page break looking mf) on the 
website 
Always ADD A SPACE BETWEEN A PAGE BREAK AND the next comment, otherwise it will appear on page --->
```
```{=html}
<!--- This is the best way to write a comment. 
It also demonstrates, you can add html directly in your rmarkdown file. See: https://www.w3schools.com/html/html_comments.asp --->
```
```{=html}
<!--- to use a multi column page we use Pandoc's fenced Div. 
see here: https://bookdown.org/yihui/rmarkdown-cookbook/multi-column.html 
But please note, we are not here to make a beautiful website, our intention is just to have a quick lab journal up and running --->
```

## Open Science

Everyone can fork this repository. I have used this example to journal my lab work and assignments.

Jochem Tolsma and Bas Hofstra use this repository for their Social Network Analysis For Social Scientists course [@SNASS]. <!--- this is a reference, stored in references.bib. It will be automatically added at the bottom of the page --->

:::

::: {.column width="50%"}
![](images/krill-issue.jpg)

Very krillaxing, isn't it?

:::
:::

**Reference:**
